Automatic Disease Diagnosis Using Large Language Models and Answer Set Programming

### 2025-06-07 paper/draft.tex
Update listing's caption

\begin{lstlisting}[caption={Excerpt from the explanation tree for the chickenpox diagnosis. The structure illustrates the reasoning path based on symptom associations.},
    label=lst:chickenpox_explanation]{Name}
    *
    |__ diagnosis(chickenpox)
        |__ has(symptom(itching))
        |__ has(symptom(fatigue))
        |__ has(symptom(lethargy))
            |__ has(symptom(fatigue))
            |__ linked_symptom(fatigue, lethargy)
        |__ has(symptom(high_fever))
            |__ has(symptom(mild_fever))
                |__ has(symptom(loss_of_appetite))
                |__ linked_symptom(loss_of_appetite, mild_fever)
            |__ linked_symptom(mild_fever, high_fever)
        |__ has(symptom(loss_of_appetite))
        |__ has(symptom(mild_fever))
            |__ has(symptom(loss_of_appetite))
            |__ linked_symptom(loss_of_appetite, mild_fever)
        |__ has(symptom(swelled_lymph_nodes))
\end{lstlisting}

>>>>

\begin{lstlisting}[caption={Excerpt from the explanation tree for the chickenpox diagnosis. The structure illustrates the reasoning path based on symptom associations (slightly modified for clarity).},
    label=lst:chickenpox_explanation]{Name}
    *
    |__ diagnosis(chickenpox)
        |__ has(symptom(itching))
        |__ has(symptom(fatigue))
        |__ has(symptom(lethargy))
            |__ has(symptom(fatigue))
            |__ linked_symptom(fatigue, lethargy)
        |__ has(symptom(high_fever))
            |__ has(symptom(mild_fever))
                |__ has(symptom(loss_of_appetite))
                |__ linked_symptom(loss_of_appetite, mild_fever)
            |__ linked_symptom(mild_fever, high_fever)
        |__ has(symptom(loss_of_appetite))
        |__ has(symptom(mild_fever))
            |__ has(symptom(loss_of_appetite))
            |__ linked_symptom(loss_of_appetite, mild_fever)
        |__ has(symptom(swelled_lymph_nodes))
\end{lstlisting}
